From heartbeat to data – Using wearable fitness trackers as an affordable approach to assess teacher stress

### 2024-12-19 02_paper/02_study/01_fitbit_paper/Submission/FitBit_submission_template.Rmd
literatur_vz
plots plots plots

  - \setcitestyle{numbers, sort&compress}

@@

df_heart_rate_std |> 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  geom_smooth(se = F,
              size = 0.5,
              colour = "black"
              ) +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  scale_x_continuous(expand = c(0.01,0)) +
  scale_y_continuous(expand = c(0, 0.25)) +
  labs(x = "",
       y = "",
       ) +
  theme_apa() + 
  facet_wrap(~ type,
             ncol = 2,
             scales = "free_y"
             ) +
  theme(plot.margin = margin(r = 30,
                             t = 20,
                             b = 5),
        text = element_text(family = "Times",
                            size = 14)
        ) -> loess_hr_std

@@

loess_comp <- annotate_figure(p = loess_comp,
                              bottom = text_grob("Time (in Minutes)",
                                                 face = "plain",
                                                 size = 14,       
                                                 family = "Times")
                              )

ggsave(loess_comp,
       filename = "plots_publication/loess_plot_std_unstd_new.pdf",
       width = 25,
       height = 14,
       units = "cm")
```

@@

```{r box plot, include=FALSE}
box_plot <-
  main_single_hr |> 
  filter(time_span != "overall") |>  
  dplyr::select("ID",
         "time_span",
         "heart_rate_std") |> 
  mutate(time_span = fct_recode(time_span,
                                "Pre-teaching Interval" = "preparation",
                                "Teaching Interval" = "teaching",
                                "Post-teaching Interval" = "post",
                                "Interview Interval" = "interview",
                                "End Interval" = "end"
                                ),
         time_span = factor(time_span,
                            levels = c("Pre-teaching Interval",
                                       "Teaching Interval",
                                       "Post-teaching Interval",
                                       "Interview Interval",
                                       "End Interval"
                                       ),
                            labels = c("Pre-Teaching\nInterval",
                                       "Teaching\nInterval",
                                       "Post-Teaching\nInterval",
                                       "Interview\nInterval",
                                       "End\nInterval")
                            )
         ) |> 
  distinct() |> 
  group_by(ID, time_span) |> 
  summarise(mean_hr_std = 
              mean(heart_rate_std, 
                   na.rm = TRUE)
            ) |> 
  ggplot(mapping = aes(x = time_span,
                       y = mean_hr_std
                       )
         ) +
  geom_boxplot()+
  scale_y_continuous(breaks=seq(-2, 2, 1), 
                     limits=c(-2, 2)
                     ) +   
  # geom_jitter(width = 0.2) +
  theme_apa() + 
  theme(text = element_text(family = "Times"),
        axis.text.x = element_text(
            color="black",
            size = 14,
            family = "Times"),
        plot.caption = element_text(hjust = 0)
        ) + 
  labs(x = "",
       y = "Mean Standardized Heart Rate",
       caption = expression(
         paste(italic("Note: N"), 
               "= 81 participants per interval. Fig. shows median (bold line), interquartile range (box) and outliers (dots)."
         )
       ))

ggsave(filename = "plots_publication/box_plot.pdf",
       plot = box_plot,
       width = 25,
       height = 14,
       units = "cm")
```

@@

plot_list_appendix <- list(
  `Preparation Phase` = list(name = "Pre-Teaching Interval", mod = mods$preparation, data = graph_data$preparation),
  `Teaching Phase` = list(name = "Teaching Interval", mod = mods$teaching, data = graph_data$teaching),
  `Post Teaching Phase` = list(name = "Post-Teaching Interval", mod = mods$post, data = graph_data$post),
  `Interview Phase` = list(name = "Interview Interval", mod = mods$interview, data = graph_data$interview),
  `End Phase` = list(name = "End Interval", mod = mods$end, data = graph_data$end)
) %>% 
  map(~ ggplot(data = .$data,
               mapping = aes(x = time,  # Use the appropriate 'x' value (like 'work_hrs' in the original)
                             y = heart_rate_std,  # Use the appropriate 'y' value (like 'inc')
                             group = ID)) +
        geom_line(mapping = aes(y = fitted(.$mod)),  # Line for fitted values from the model
                  color = "blue",  # Adjust color for clarity
                  size = 1) +  # Line thickness
        geom_point(alpha = 0.5, size = 0.5) +  # Points with transparency and size
        facet_wrap(~ ID, nrow = 8) +  # Arrange plots by 'ID'
        xlab('Time (in Minutes)') +  # X-axis label (similar to 'Arbeitsstunden pro Woche')
        ylab('Heart Rate (Standardized)') +  # Y-axis label (similar to 'Nettoeinkommen')
        scale_x_continuous(breaks = c(0, 5, 10)) +  # Customize x-axis breaks as needed
        #labs(title = .$name) +  # Title for each plot based on phase name
        theme_bw() + # Use a clean theme
        theme(text = element_text(family = "Times",
                                  size = 14)
              )
      )

@@

ggsave(preparation_plot,
       filename = "plots_publication/plot_preparation_appendix.pdf",
       width = 25,
       height = 29,
       units = "cm")

ggsave(teaching_plot,
       filename = "plots_publication/plot_teaching_appendix.pdf",
       width = 25,
       height = 29,
       units = "cm")

ggsave(post_teaching_plot,
       filename = "plots_publication/plot_post_teaching_appendix.pdf",
       width = 25,
       height = 29,
       units = "cm")

ggsave(interview_plot,
       filename = "plots_publication/plot_interview_appendix.pdf",
       width = 25,
       height = 29,
       units = "cm")

ggsave(end_plot,
       filename = "plots_publication/plot_end_appendix.pdf",
       width = 25,
       height = 29,
       units = "cm")

>>>>

  - \setcitestyle{numbers}

@@

df_heart_rate_std |> 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  geom_smooth(se = F,
              size = 0.5,
              colour = "black"
              ) +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  scale_x_continuous(expand = c(0.01,0)) +
  scale_y_continuous(expand = c(0, 0.25)) +
  labs(x = "",
       y = "",
       ) +
  theme_apa() + 
  facet_wrap(~ type,
             ncol = 2,
             scales = "free_y"
             ) +
  theme(plot.margin = margin(r = 30,
                             t = 20,
                             b = 5),
        text = element_text(family = "Sans-Serif",
                            size = 14)
        ) -> loess_hr_std

@@

loess_comp <- annotate_figure(p = loess_comp,
                              bottom = text_grob("Time (in Minutes)",
                                                 face = "plain",
                                                 size = 14,       
                                                 family = "Sans-Serif")
                              )

ggsave(loess_comp,
       filename = "plots_publication/loess_plot_std_unstd_new.svg",
       width = 25,
       height = 14,
       units = "cm")
```

@@

```{r box plot, include=FALSE}
box_plot <-
  main_single_hr %>% 
  filter(time_span != "overall") %>%
  dplyr::select("ID",
         "time_span",
         "heart_rate_std") %>% 
  mutate(time_span = fct_recode(time_span,
                                "Pre-teaching Interval" = "preparation",
                                "Teaching Interval" = "teaching",
                                "Post-teaching Interval" = "post",
                                "Interview Interval" = "interview",
                                "End Interval" = "end"
                                ),
         time_span = factor(time_span,
                            levels = c("Pre-teaching Interval",
                                       "Teaching Interval",
                                       "Post-teaching Interval",
                                       "Interview Interval",
                                       "End Interval"
                                       ),
                            labels = c("Pre-Teaching\nInterval",
                                       "Teaching\nInterval",
                                       "Post-Teaching\nInterval",
                                       "Interview\nInterval",
                                       "End\nInterval")
                            )
         ) %>%
  distinct() %>% 
  group_by(ID, time_span) %>%
  summarise(mean_hr_std = 
              mean(heart_rate_std, 
                   na.rm = TRUE)
            ) %>% 
  ggplot(mapping = aes(x = time_span,
                       y = mean_hr_std
                       )
         ) +
  geom_boxplot() +
  stat_summary(
    fun = mean, geom = "point", 
    shape = 4, size = 3, color = "red" # Mean as red "x"
  ) +
  stat_summary(
    fun.data = mean_sdl, 
    fun.args = list(mult = 1), 
    geom = "errorbar", 
    width = 0.2, color = "blue" # SD as blue error bars
  ) +
scale_y_continuous(breaks=seq(-2, 2, 1), 
                     limits=c(-2, 2)
                     ) +
  theme_apa() + 
  theme(axis.text.x = 
          element_text(family = 'Sans-Serif',
            color="black",
            size = 12),
        plot.caption = element_text(hjust = 0)
        ) + 
  labs(x = "",
       y = "Mean Standardized Heart Rate Level"
         )

ggsave(filename = "plots_publication/box_plot.svg",
       plot = box_plot,
       width = 25,
       height = 14,
       units = "cm")
```

@@

plot_list_appendix <- list(
  `Preparation Phase` = list(name = "Pre-Teaching Interval", mod = mods$preparation, data = graph_data$preparation),
  `Teaching Phase` = list(name = "Teaching Interval", mod = mods$teaching, data = graph_data$teaching),
  `Post Teaching Phase` = list(name = "Post-Teaching Interval", mod = mods$post, data = graph_data$post),
  `Interview Phase` = list(name = "Interview Interval", mod = mods$interview, data = graph_data$interview),
  `End Phase` = list(name = "End Interval", mod = mods$end, data = graph_data$end)
) %>% 
  map(~ ggplot(data = .$data,
               mapping = aes(x = time,  # Use the appropriate 'x' value (like 'work_hrs' in the original)
                             y = heart_rate_std,  # Use the appropriate 'y' value (like 'inc')
                             group = ID)) +
        geom_line(mapping = aes(y = fitted(.$mod)),  # Line for fitted values from the model
                  color = "blue",  # Adjust color for clarity
                  size = 1) +  # Line thickness
        geom_point(alpha = 0.5, size = 0.5) +  # Points with transparency and size
        facet_wrap(~ ID, nrow = 8) +  # Arrange plots by 'ID'
        xlab('Time (in Minutes)') +  # X-axis label (similar to 'Arbeitsstunden pro Woche')
        ylab('Heart Rate (Standardized)') +  # Y-axis label (similar to 'Nettoeinkommen')
        ylim(-4, 4) +
        scale_x_continuous(breaks = c(0, 5, 10)) +  # Customize x-axis breaks as needed
        #labs(title = .$name) +  # Title for each plot based on phase name
        theme_bw() + # Use a clean theme
        theme(text = element_text(size = 14,
                                  family = 'Sans-Serif')
              )
      )

@@

ggsave(preparation_plot,
       filename = "plots_publication/plot_preparation_appendix.svg",
       width = 25,
       height = 29,
       units = "cm")

ggsave(teaching_plot,
       filename = "plots_publication/plot_teaching_appendix.svg",
       width = 25,
       height = 29,
       units = "cm")

ggsave(post_teaching_plot,
       filename = "plots_publication/plot_post_teaching_appendix.svg",
       width = 25,
       height = 29,
       units = "cm")

ggsave(interview_plot,
       filename = "plots_publication/plot_interview_appendix.svg",
       width = 25,
       height = 29,
       units = "cm")

ggsave(end_plot,
       filename = "plots_publication/plot_end_appendix.svg",
       width = 25,
       height = 29,
       units = "cm")
